% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\author{}
\date{}

\begin{document}

\hypertarget{henrik-zenkert}{%
\section{Henrik Zenkert}\label{henrik-zenkert}}

\begin{itemize}
\tightlist
\item
  henrik.zenkert@gmail.com
\item
  +45 31414643
\item
  Islands Brygge 60, 2300, Copenhagen
\end{itemize}

\hypertarget{educationuddannelse}{%
\subsection{Education/Uddannelse}\label{educationuddannelse}}

\textbf{Diplomingeniør Softwareteknologi \textbar{} \emph{2021-}}

Danmarks Tekniske Universitet \textbar{} Kongens Lyngby, Danmark

\textbf{Objektorienterad programmering och design \textbar{}
\emph{2019}}

Luleå tekniska universitet \textbar{} Luleå, Sverige

\hypertarget{projectsprojekter}{%
\subsection{Projects/Projekter}\label{projectsprojekter}}

\hypertarget{operadocs}{%
\subsubsection{Operadocs}\label{operadocs}}

\href{https://operadocs.com/}{Link} \textbar{}
\href{https://github.com/YesSeri/opera-docs}{GitHub}

This is a webpage where you can find sheet music for free for operas.
Having worked as an opera singer for many years, I know how hard it can
be to find the correct sheet music, quickly. All the scores I upload are
no longer under copyright protection.

\begin{itemize}
\tightlist
\item
  Next.js
\item
  MySQL
\item
  Python
\end{itemize}

\hypertarget{bubblewrap}{%
\subsubsection{Bubblewrap}\label{bubblewrap}}

\href{https://yesseri.github.io/bubblewrap.html}{Link} \textbar{}
\href{https://github.com/YesSeri/bubble-wrap}{GitHub}

A game written in Rust and Wasm. Survive the bubbles that attack you.
Everything is written from scratch, no game engine or things like that.
Wasm4 contains a set of basic functions such as painting rectangles and
setting individual pixels to one of four chosen colors. Play with arrow
keys and Z and X.

\begin{itemize}
\tightlist
\item
  Rust
\item
  I made a wrapper game engine around wasm4
\end{itemize}

\hypertarget{pianisto}{%
\subsubsection{Pianisto}\label{pianisto}}

\href{https://pianisto.net/}{Link} \textbar{}
\href{https://github.com/YesSeri/svelte-piano}{GitHub}

A piano that you can play online. It is written in Svelte and uses the
Tone.js library. It was inspired by the piano app Real Piano. I wanted
to create an ad-free alternative.

\begin{itemize}
\tightlist
\item
  HTML
\item
  CSS
\item
  Javascript
\end{itemize}

\hypertarget{work-experienceerhvervserfaring}{%
\subsection{Work
Experience/Erhvervserfaring}\label{work-experienceerhvervserfaring}}

\hypertarget{it-consultant---zenjon-ab-2018-2022}{%
\subsubsection{IT consultant - Zenjon AB
2018-2022}\label{it-consultant---zenjon-ab-2018-2022}}

\begin{itemize}
\tightlist
\item
  Going through code submissions and look for plagiarized material.
\item
  Setting up scripts for more efficiently processing spam. Primarily
  done in JavaScript and GreaseMonkey to make the internal systems more
  efficient.
\item
  Admin duties, checking for plagiarism, monitoring spam comments.
\end{itemize}

\end{document}
